Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation rainforest of India

### 2018-11-19 draft.Rmd
Uppangala 0.1.9053 Plot map, CE figure, PCA figure, strata statistics

```{r Uppangala, fig.cap="Canopy model of the 10-ha forest permanent plot in Uppangala, India. Preliminry figure to be improved."}
DCM <- raster("./data/Canopy.tif")
crs(DCM) <- '+proj=utm +zone=43 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0'
DEM <- raster("./data/DEM.tif")
crs(DEM) <- '+proj=utm +zone=43 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0'
limits <- shapefile("./data/Plots/Shapeall10ha.shp")
DCM <- crop(DCM, limits)
DEM <- crop(DEM, limits)
DEM_spdf <- as(DEM, "SpatialPixelsDataFrame")
DEM_df <- as.data.frame(DEM_spdf)
colnames(DEM_df) <- c("Elevation", "x", "y")
DEM_plot <- ggplot() +  
  geom_tile(data=DEM_df, aes(x=x, y=y, fill=Elevation), alpha=0.8) + 
  scale_fill_distiller(palette = "Spectral") +
  coord_equal() +
  cowplot::theme_map()
DCM_spdf <- as(DCM, "SpatialPixelsDataFrame")
DCM_df <- as.data.frame(DCM_spdf)
colnames(DCM_df) <- c("Height", "x", "y")
DCM_plot <- ggplot() +  
  geom_tile(data=DCM_df, aes(x=x, y=y, fill=Height), alpha=0.8) + 
  coord_equal() +
  cowplot::theme_map() +
  scale_fill_distiller(palette = "Spectral")
ggsave(cowplot::plot_grid(DEM_plot, DCM_plot, labels = c("a) Elevation (m)", "b) Canopy height (m)")), 
       file = "Plot.png",
       path = './data/',
       width = 200, height = 100, unit = 'mm',
       dpi = 300)
```

@@

```{r PCA,  fig.cap='Principal Component Analysis (PCA) of species mean trait values. Marginal plots represent the density distribution of species on the two principal component axis for each strata. See table \\@ref(tab:Traits) for abbreviation.'}
pca.plot <- autoplot(PFT.pca, 
         data = Q %>% 
           left_join(L %>% 
                       dplyr::select(-com) %>% 
                       summarise_all(sum) %>% 
                       t() %>% 
                       data.frame() %>% 
                       rename(abundance =  ".") %>% 
                       mutate(SpCode = row.names(.))) %>% 
           filter(!is.na(WES)), 
         colour = "strata",
         size = "abundance",
         loadings.label.size = 6,
         loadings.label.colour = 'black',
         loadings = T, loadings.label = T, loadings.colour = 'black',
         loadings.label.vjust = 1.2) +
  coord_equal() +
  geom_hline(aes(yintercept = 0), col = 'green', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'purple', linetype = "dotted") +
  xlab('Axe 1 − 33.66 %') + ylab('Axe 2 − 29.07 %') +
  theme(legend.position = c(1, 1), 
        legend.justification = c(1, 1))
spectrum.density <-pca.plot$data %>% 
  select(Comp.1, Comp.2, strata) %>% 
  rename(WES = Comp.1, LES = Comp.2) %>% 
  melt(id.vars = "strata", variable.name = "spectrum") %>% 
  ggplot(aes(value, color = spectrum, fill = spectrum)) +
  geom_density(alpha = 0.5) + 
  facet_wrap(~strata, nrow = 2) +
  coord_flip() +
  scale_fill_manual("PCA axis", 
                    labels = c("WES" = "PCA1", "LES" = "PCA2"),
                    values = c("green", "purple")) +
  scale_color_manual("PCA axis", 
                     labels = c("WES" = "PCA1", "LES" = "PCA2"),
                     values = c("green", "purple"))
cowplot::plot_grid(pca.plot, spectrum.density, rel_widths = c(2,1))
```

@@

@@

>>>>

```{r Uppangala, fig.cap="Canopy model of the 10-ha forest permanent plot in Uppangala, India. Preliminry figure to be improved."}
DCM <- raster("./data/Canopy.tif")
crs(DCM) <- '+proj=utm +zone=43 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0'
DEM <- raster("./data/DEM.tif")
crs(DEM) <- '+proj=utm +zone=43 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0'
limits <- shapefile("./data/Plots/Shapeall10ha.shp")
limits$melt <- 1
limits <- maptools::unionSpatialPolygons(limits, limits$melt)
DCM <- crop(DCM, buffer(limits, 30))
DEM <- crop(DEM, buffer(limits, 30))
DEM <- as(DEM, "SpatialPixelsDataFrame")
DEM <- as.data.frame(DEM)
colnames(DEM) <- c("Elevation", "x", "y")
DCM <- as(DCM, "SpatialPixelsDataFrame")
DCM <- as.data.frame(DCM)
colnames(DCM) <- c("Height", "x", "y")
ggplot() +  
  geom_tile(data=DCM, aes(x=x, y=y, fill=Height)) +
  geom_contour(data=DEM, aes(x=x, y=y, z=Elevation),
               colour = "black", alpha = 0.6, breaks = seq(300, 500, by = 25)) +
  directlabels::geom_dl(data=DEM, aes(x=x, y=y, z=Elevation, label = paste0(..level.., "m")),
                        method = list('last.bumpup', cex = 0.8, hjust = 1),
                        stat="contour", breaks = seq(300, 500, by = 25)) +
  geom_polygon(data = fortify(limits),
                 aes(long, lat, group=group),
                 colour = "black", lwd = 1.1, alpha = 0) +
  coord_equal() +
  cowplot::theme_map() +
  scale_fill_distiller("Canopy\nheight (m)", palette = "Spectral") +
  ggsave(file = "Plot.png",
         path = './data/',
         width = 150, height = 200, unit = 'mm',
         dpi = 300)
rm(DEM, DCM, limits, contour, DEM_df, DCM_df, DEM_spdf, DCM_spdf, DCM_plot, DEM_plot)
```

@@

```{r PCA,  fig.cap='Principal Component Analysis (PCA) of species mean trait values. Marginal plots represent the density distribution of species on the two principal component axis for each strata. See table \\@ref(tab:Traits) for abbreviation.'}
pca.plot <- autoplot(PFT.pca, 
         data = Q %>% 
           left_join(L %>% 
                       dplyr::select(-com) %>% 
                       summarise_all(sum) %>% 
                       t() %>% 
                       data.frame() %>% 
                       rename(abundance =  ".") %>% 
                       mutate(SpCode = row.names(.))) %>% 
           filter(!is.na(WES)), 
         colour = "strata",
         size = "abundance",
         loadings.label.size = 6,
         loadings.label.colour = 'black',
         loadings = T, loadings.label = T, loadings.colour = 'black',
         loadings.label.vjust = 1.2) +
  coord_equal() +
  geom_hline(aes(yintercept = 0), col = 'green', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'purple', linetype = "dotted") +
  xlab('Axe 1 − 33.66 %') + ylab('Axe 2 − 29.07 %') +
  theme(legend.position = c(1, 1), 
        legend.justification = c(1, 1))
spectrum.density <- pca.plot$data %>%
  select(Comp.1, Comp.2, strata) %>%
  rename(WES = Comp.1, LES = Comp.2) %>%
  melt(id.vars = "strata", variable.name = "spectrum") %>%
  ggplot(aes(value, color = spectrum, fill = spectrum)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~strata, nrow = 2) +
  coord_flip() +
  scale_fill_manual("PCA axis",
                    labels = c("WES" = "PCA1", "LES" = "PCA2"),
                    values = c("green", "purple")) +
  scale_color_manual("PCA axis",
                     labels = c("WES" = "PCA1", "LES" = "PCA2"),
                     values = c("green", "purple"))
spectrum.boxplots <- pca.plot$data %>%
  select(Comp.1, Comp.2, strata) %>%
  rename(`Axe 1` = Comp.1, `Axe 2` = Comp.2) %>%
  melt(id.vars = "strata", variable.name = "spectrum") %>%
  ggplot(aes(strata, value, fill = strata)) +
  ggpubr::stat_compare_means(aes(label = ..p.signif..)) +
  geom_boxplot() +
  facet_wrap(~spectrum, nrow = 2)
# cowplot::plot_grid(pca.plot, spectrum.density, rel_widths = c(2,1))
ggsave(cowplot::plot_grid(pca.plot, spectrum.boxplots, rel_widths = c(2,1), labels = c("A", "B")), 
       file = "PCA.png",
       path = './data/',
       width = 200, height = 150, unit = 'mm',
       dpi = 300)
```

@@

```{r GMboxplot, fig.cap="Boxplot of guilds means (GM) among communties for each traits (for canopy (C) and understorey (U) guilds). See table \\@ref(tab:Traits) for abbreviations.", fig.height=4}
L %>%
  melt(id.var = "com",
       variable.name = "SpCode",
       value.name = "abundance") %>% 
  mutate(abundance = ifelse(abundance > 0, 1, 0)) %>% 
  dcast(SpCode ~ com, value.var = "abundance") %>% 
  mutate(SpCode = as.character(SpCode)) %>% 
  inner_join(Q, by = "SpCode") %>%
  select(-SpCode) %>%
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>%
  group_by(strata, community) %>%
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>% 
  select(-community) %>% 
  melt(id.vars = "strata", 
       variable.name = "trait",
       value.name = "GM") %>% 
  ggplot(aes(x = strata, y = GM, fill = strata)) +
  geom_boxplot() +
  facet_wrap(~trait, scales = "free", nrow = 2) +
  xlab("Guild") + scale_fill_discrete(guide = "none") +
  ggpubr::stat_compare_means(aes(label = paste(..p.signif..))) 
```

@@

## S4 : Dawkins effect on traits

```{r CEeffect}
# L %>% 
#   melt(id.vars = "com",
#        variable.name = "SpCode",
#        value.name = "individuals") %>% 
#   filter(individuals > 0) %>% 
#   left_join(Q %>% 
#               select(SpCode, strata)) %>% 
#   filter(!is.na(strata)) %>% 
#   group_by(com, strata) %>% 
#   summarise(species = length(unique(SpCode)),
#             individuals = sum(individuals)) %>% 
#   ungroup() %>% 
#   # group_by(strata) %>% 
#   summarise(species = mean(species), individuals = mean(individuals))
# genPFT() %>%
#   mutate(CE = gsub('([[:alpha:]])', "", CE)) %>%
#   filter(!is.na(CE)) %>%
#   mutate(LA = log(LA)) %>%
#   mutate(SLA = log(SLA)) %>%
#   select(CE, Sp, WD, LT, LA, LDMC, LTD, SLA) %>%
#   reshape2::melt(id.vars = c("CE", "Sp"), variable.name = "Trait") %>%
#   group_by(Trait) %>%
#   do(anova = TukeyHSD(aov(lm(value ~ CE, data = .)))) %>%
#   tidy(anova) %>%
#   filter(adj.p.value < 0.05)
my_comparisons <- list( c("1", "2"), c("2", "3"), c("3", "4"),
                        c("4", "5"), c("1", "3"), c("3", "5"),
                        c("1", "5"),  c("2", "4"), c("2", "5"))
genPFT() %>% 
  mutate(CE = gsub('([[:alpha:]])', "", CE)) %>% 
  filter(!is.na(CE)) %>% 
  select(CE, WD, LT, LA, LDMC, LTD, SLA) %>% 
  mutate(LA = log(LA)) %>% 
  mutate(SLA = log(SLA)) %>% 
  reshape2::melt(id.vars = "CE", variable.name = "Trait") %>% 
  ggplot(aes(CE, value, fill = CE)) +
  geom_boxplot() +
  facet_wrap(~Trait, scales = "free") +
  ggpubr::stat_compare_means(comparisons = my_comparisons, aes(label = ..p.signif..)) +
  ggpubr::stat_compare_means(method = "anova", aes(label = paste("Anova", ..p.signif..))) +
  ggsave(file = "CE.png",
         path = './data/',
         width = 200, height = 200, unit = 'mm',
         dpi = 300)

genPFT() %>% 
  select(CE) %>% 
  mutate(CE = gsub('([[:alpha:]])', "", CE)) %>% 
  group_by(CE) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(P = round(n/sum(n)*100))
```
